---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

![](https://img.shields.io/github/r-package/v/JesseAlderliesten/MontyHall?color=blue)


# MontyHall
With `MontyHall` you can simulate the Monty Hall game as an illustration of
simulation studies.

This package is still under development and thus *unstable*.

## Installation
You can install `MontyHall` from
[GitHub](https://github.com/JesseAlderliesten/MontyHall) with:
    
```{r, eval = FALSE}
if(!requireNamespace("remotes", quietly = TRUE)) {
  install.packages(pkgs = "remotes", quiet = FALSE)
}
remotes::install_github(repo = "JesseAlderliesten/MontyHall", dependencies = TRUE,
                        upgrade = FALSE, force = FALSE, quiet = FALSE,
                        build_vignettes = TRUE, lib = NULL,
                        verbose = getOption("verbose"))
```

For information about installing and configuring R and RStudio, see my
repository [checkrpkgs](https://github.com/JesseAlderliesten/checkrpkgs).


## Examples
Play a typical game a hundred times, and show the fraction of games won if the
participant sticks to the original choice or changes to another door:

```{r play_MontyHall_repeated}
library(MontyHall)
set.seed(314)

many_games <- play_MontyHall_repeated(n_doors = 3, n_prizes = 1, n_games = 100)
length(which(many_games$stick)) / length(many_games$stick)
length(which(many_games$change)) / length(many_games$change)
```

The results of `play_MontyHall()` are stochastic, i.e., every time you use it
you will get different results (unless you run `set.seed(314)` that sets the
random seed, which I used to make results reproducible). To show how the
stochasticity influences the results, the simulation is repeated fifty times and
the results are summarised:

```{r plot_MontyHall_repeated}
library(MontyHall)
set.seed(314)
plot_MontyHall_repeated(n_doors = 3, n_prizes = 1, n_games = 100, n_trials = 50,
                        sort_values = TRUE, show_ranges = TRUE,
                        print_summary = TRUE)
```

The different steps in the game can also be performed individually to get more
details. 

```{r play_MontyHall, typical game}
library(MontyHall)
set.seed(314)

play_MontyHall(n_doors = 3L, n_prizes = 1L)

# Same as:
set.seed(314)
(setup <- setup_MontyHall(n_doors = 3L, n_prizes = 1L))
(chosen_door <- choose_door(status = setup$status))
(new_status <- reveal_door(status = setup$status, prize = setup$prize,
                           chosen_door = chosen_door))
(outcome(status = new_status, prize = setup$prize,
         chosen_door = chosen_door))
```

Play a single game with a ten doors and three prizes.  
NB. Currently only a single door is opened before the contestant gets the choice
to stick to the originally chosen door or change to another door.

```{r play_MontyHall, manydoors}
library(MontyHall)
set.seed(314)

play_MontyHall(n_doors = 10L, n_prizes = 3L)

# Same as:
set.seed(314)
(setup <- setup_MontyHall(n_doors = 10L, n_prizes = 3L))
(chosen_door <- choose_door(status = setup$status))
(new_status <- reveal_door(status = setup$status, prize = setup$prize,
                           chosen_door = chosen_door))
(outcome(status = new_status, prize = setup$prize,
         chosen_door = chosen_door))
```

# Alternatives
Many packages for Monty Hall simulations exist on [GitHub](https://github.com/).
I have not yet browsed through them.
